Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
lmm 5.1
lmm4.1

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.}
First, we prove that $\cross_{R_{k-2}}(\bm{t})$ is non-empty for each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$. Let $\bm{t} = (r_1,...,r_{k-3},h',v)$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ that covers both the left endpoint of $h$ and the right endpoint of $h'$. Thus, $r_{k-2}$ contains $h'$, because $h'$ shares the same left endpoint as $h$. Since the effective horizontal segment of $\bm{t}$ is contained in $h'$, it is also covered by $r_{k-2}$. This implies that $\cross_{R_{k-2}}(\bm{t})$ includes $r_{k-2}$, and is therefore non-empty.

@@

Then, we resorts to the algorithm generate-$\J_2$ (see Section~\ref{sec:hv:type2}). For each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$, this algorithm adds to $\J_2$ exactly $|\cross_{R_{k-2}}(\bm{t})|\geq 1$ tuples. Therefore, $|\J(R_1, ..., R_{k-3}, H', V)| \le |\J_2| \le \out$, where the last inequality follows from the definition of $\J_2$ (see \eqref{eqn:hv:type2:J2}).

>>>>

\extraspacing \noindent {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.}
First, we prove that $\cross_{R_{k-2}}(\bm{t})$ is non-empty for each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $\bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ that covers both the left endpoint of $h$ and the right endpoint of $h'$. Thus, $r_{k-2}$ contains $h'$, because $h'$ shares the same left endpoint as $h$. Since the effective horizontal segment of $\bm{t}$ is contained in $h'$, it is also covered by $r_{k-2}$. This implies that $\cross_{R_{k-2}}(\bm{t})$ includes $r_{k-2}$, and is therefore non-empty.

@@

Then, we resorts to the algorithm generate-$\J_2$ (see Section~\ref{sec:hv:type2}). For each tuple $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$, this algorithm adds to $\J_2$ exactly $|\cross_{R_{k-2}}(\bm{t})|\geq 1$ tuples. 
By the correctness of the algorithm, we have $|\J(R_1,...,R_{k-3},H',V)| \le |\J_2| \le \out$, where the last inequality follows from the definition of $\J_2$ (see \eqref{eqn:hv:type2:J2}).
